\textbf{The Illusion Game: A Novel Experimental Paradigm Provides Evidence in Favour of a General Factor of Visual Illusion Sensitivity and Personality Correlates}

### 2022-09-07 manuscript.Rmd
remove duplicate ref

Visual illusions are fascinating stimuli, capturing a key feature of our neurocognitive systems. They eloquently show that our brains did not evolve to be perfect perceptual devices providing veridical accounts of physical reality, but integrate prior knowledge and contextual information - blended together in our subjective conscious experience [@carbon2014]. Despite the historical and intensive interest within the fields of visual perception [@day1972; @eagleman2001; @gomez-villa2022], consciousness science [@caporuscio2022; @lamme2020], and psychiatry [@notredame2014; @gori2016; @razeghi2022; @teufel2015], several important issues remain open.

Notably, the presence of a common mechanism underlying the effect of different illusions has been contested [@hamburger2016; @cretenoud2019a; @teufel2018a; @cretenoud2020]; and the nature of the underlying processes - whether related to low-level features of the visual processing system [@cretenoud2019; @gori2016] or to top-down influences of prior beliefs [@teufel2018; @caporuscio2022] are strongly debated. The existence of dispositional correlates of illusion sensitivity - for example, higher illusion resistance has been reported in schizophrenia and autism [@notredame2014; @park2022; @giaouri2011; @keane2014; @pessoa2008], as well as in individuals with stronger traits of aggression and narcissism [@zhang2017; @konrath2009seeing] - is another area of controversy.

@@

Indeed, many visual illusions can be seen as being composed of *targets* (e.g., same-length lines), of which perception is biased by the *context* (e.g., in the Müller-Lyer illusion, the same-length line segments appear to have different lengths when they end with inwards or outwards pointing arrows). Past illusion studies traditionally employed paradigms focusing on participants' subjective experience, by asking them to what extent they perceive two identical targets as different [@lanyi2022can], or having them adjust the targets to a reference stimulus relying only on their perception [@mylniec2016a; @grzeczkowski2018]. Alternatively, *Pyllusion* allows the creation of illusions in which the targets are objectively different (e.g., one segment is truly more or less longer than the other), and in which the illusion varies in strength (the biasing angle of the arrows is more or less acute).

>>>>

Visual illusions are fascinating stimuli capturing a key feature of our neurocognitive systems. They eloquently show that our brains did not evolve to be perfect perceptual devices providing veridical accounts of physical reality, but integrate prior knowledge and contextual information - blended together in our subjective conscious experience [@carbon2014]. Despite the historical and intensive interest within the fields of visual perception [@day1972; @eagleman2001; @gomez-villa2022], consciousness science [@caporuscio2022; @lamme2020], and psychiatry [@notredame2014; @gori2016; @razeghi2022; @teufel2015], several important issues remain open.

Notably, the presence of a common mechanism underlying the effect of different illusions has been contested [@hamburger2016; @cretenoud2019a; @teufel2018a; @cretenoud2020]; and the nature of the underlying processes - whether related to low-level features of the visual processing system [@cretenoud2019; @gori2016] or to top-down influences of prior beliefs [@teufel2018; @caporuscio2022] are strongly debated. The existence of dispositional correlates of illusion sensitivity - for example, higher illusion resistance has been reported in schizophrenia and autism [@notredame2014; @park2022; @giaouri2011; @keane2014; @pessoa2008], as well as in individuals with stronger aggression and narcissism traits [@zhang2017; @konrath2009seeing] - is another area of controversy.

@@

Indeed, many visual illusions can be seen as being composed of *targets* (e.g., same-length lines), of which perception is biased by the *context* (e.g., in the Müller-Lyer illusion, the same-length line segments appear to have different lengths when they end with inwards or outwards pointing arrows). Past illusion studies traditionally employed paradigms focusing on participants' subjective experience, by asking them to what extent they perceive two identical targets as different [@lanyi2022can], or having them adjust the targets to a reference stimulus relying only on their perception [@mylniec2016; @grzeczkowski2018]. Alternatively, *Pyllusion* allows the creation of illusions in which the targets are objectively different (e.g., one segment is truly more or less longer than the other), and in which the illusion varies in strength (the biasing angle of the arrows is more or less acute).
